---
title: "README"
output: md_document
---

# edgar 2.1.0
Tool for the U.S. SEC EDGAR Retrieval and Parsing of Corporate Filings

# Overview
In the USA, companies file different forms with the U.S. Securities and Exchange Commission (SEC) through EDGAR (Electronic Data Gathering, Analysis, and Retrieval system). The EDGAR database automated system collects all the different necessary filings and makes it publicly available. This package facilitates retrieving, storing, searching, and parsing of all the available filings on the EDGAR server. It downloads filings from SEC server in bulk with a single query. Additionally, it provides various useful functions: extracts 8-K triggering events, extract "Business (Item 1)" and "Management's Discussion and Analysis(Item 7)" sections of annual statements, searches filings for desired keywords, provides sentiment measures, parses filing header information, and provides HTML view of SEC filings. 

# Installation
The package is maintained on
[github](https://github.com/grlju/edgar).

You can install the latest version of the edgar R package from
[github](https://github.com/grlju/edgar)

```{r}
library("edgar")
```

# Implementation of the edgar package

## SEC guidelines on downloading EDGAR files
Please download only what you need and moderate download requests to minimize EDGAR server load. A user is required to declare user agent in request headers. The following link explains these requirements in details.
https://www.sec.gov/os/accessing-edgar-data

Accordingly, `edgar` package requires user to pass user agent in every function. It should be in the form of 
```{r}
useragent = "Your_Name_Contact@domain.com"
```

## Download daily filing information
The `getDailyMaster` function takes date as an input parameter from a user, and downloads master index for the date from the U.S. SEC EDGAR server https://www.sec.gov/Archives/edgar/daily-index/. It strips headers and converts this daily filing information into dataframe format. Function creates new directory 'Daily Indexes' into working directory to save these downloaded daily master index files in Rda format.

```{r}
output <- getDailyMaster('08/09/2016', useragent)
head(output)
```

## Download quarterly filing information
The `getMasterIndex` function takes filing year as an input parameter from a user, downloads quarterly master indexes from the US SEC server https://www.sec.gov/Archives/edgar/full-index/. It then strips headers from the master index files, converts them into dataframe, and merges such quarterly dataframes into yearly dataframe, and stores them in Rda format. It has ability to download master indexes for multiple years based on the user input. This function creates a new directory `Master Indexes` into current working directory to save these Rda Master Index. Please note, for all other functions in this package need to locate the same working directory to access these Rda master index files.
```{r}
getMasterIndex(2006, useragent)
load("edgar_MasterIndex/2006master.Rda")  # Load the generated yearly filing information
head(year.master)
```
## Search for filing information
The `getFilingInfo` function takes firm identifier (name or cik), filing year(s), quarter(s), and form type as input parameters from a user and provides filing information for the firm. The function automatically downloads master index for the input year(s) and the quarter(s) using `getMasterIndex` function if it is not already been downloaded in the current working directory. By default, information of all the form types filed in all the quarters of the input year by the firm will be provided by this function.
```{r}
info <- getFilingInfo('United Technologies', c(2005, 2006), quarter = c(1,2), form.type = c('8-K','10-K'), useragent) 

head(info)
```

## Download filings
The `getFilings` function takes CIKs, form type, filing year, and quarter of the filing as input. It creates new directory `Edgar filings_full text` to store all downloaded filings. All the filings will be stored in the current working directory. Keep the same current working directory for further process.
```{r}
output <- getFilings(cik.no = c(1000180, 38079), c('10-K','10-Q'), 2006, quarter = c(1, 2, 3), downl.permit = "y", useragent)

output
```

## Get HTML view of filings
The `getFilingsHTML` function takes CIK(s), form type(s), filing year(s), and quarter of the filing as input. The function imports edgar filings downloaded via getFilings function; otherwise, it downloads the filings which are not already been downloaded. It then reads the downloaded filings, scraps filing text excluding exhibits, and saves the filing contents in `Edgar filings_HTML view` directory in HTML format.
```{r}
output <- getFilingsHTML(cik.no = c(1000180, 38079), c('10-K','10-Q'), 2006, quarter = c(1, 2, 3), useragent)

head(output)
```

## Extract filing header information
The `getFilingHeader` function takes CIK(s), form type(s), and year(s) as input parameters. The function first imports available downloaded filings in local woking directory `Edgar filings_full text` created by getFilings function; otherwise, it automatically downloads the filings which are not already been downloaded. It then parses all the important header information from filings. The function returns a dataframe with filing and header information.
```{r}
header.df <- getFilingHeader(cik.no = c('1000180', '38079'), form.type = '10-K', filing.year = 2006, useragent) 

header.df
```

## Search filings for input keywords
The `searchFilings` function takes search keyword vector, CIK(s), form type(s), and year(s) as input parameters. The function first imports available downloaded filings in the local woking directory `Edgar filings_full text` created by `getFilings` function; otherwise, it automatically downloads the filings which are not already been downloaded. It then reads the filings and searches for the input keywords. The function returns a dataframe with filing information and the number of keyword hits. Additionally, it saves the search information with surrounding content of search keywords in HTML format in the new directory `Keyword search results`. These HTML view of search results would help the user to analyze the search strategy and identify false positive hits.
```{r}
word.list = c('derivative','hedging','currency forwards','currency futures')
output <- searchFilings(cik.no = c('1000180', '38079'), form.type = c("10-K", "10-K405","10KSB", "10KSB40"), filing.year = c(2005, 2006), word.list, useragent) 

output
```

## Extract business description section from annual statements
The `getBusinDescr` function takes firm CIK(s) and filing year(s) as input parameters from a user and provides "Item 1" section extracted from annual statements along with filing information. The function imports annual filings (10-K statements) downloaded via `getFilings` function; otherwise, it automates the downloading process if not already been downloaded. It then reads the downloaded statements, cleans HTML tags, and parse the contents. This function automatically creates a new directory with the name `Business descriptions text` in the current working directory and saves scrapped business description sections in this directory. It considers "10-K", "10-K405", "10KSB", and "10KSB40" form types as annual statements.
```{r}
output <- getBusinDescr(cik.no = c(1000180, 38079), filing.year = c(2005, 2006), useragent)

output
```

## Extract MD&A section from annual statements
The `getMgmtDisc` function takes firm CIK(s) and filing year(s) as input parameters from a user and provides "Item 7" section extracted from annual statements along with filing information. The function imports annual filings downloaded via `getFilings` function; otherwise, it downloads the filings which are not already been downloaded. It then reads, cleans, and parse the required section from the filings. It creates a new directory with the name `MD&A section text` in the current working directory to save scrapped "Item 7" sections in text format. It considers "10-K", "10-K405", "10KSB", and "10KSB40" form types as annual statements.
```{r}
output <- getMgmtDisc(cik.no = c(1000180, 38079), filing.year = 2005, useragent)

output
```

## Retrieve Form 8-K items information
The `get8KItems` function takes firm CIK(s) and filing year(s) as input parameters from a user and provides information on the Form 8-K triggering events along with the firm filing information. The function searches and imports existing downloaded 8-K filings in the current directory; otherwise it downloads them using `getFilings` function. It then reads the 8-K filings and parses them to extract events information.
```{r}
output <- get8KItems(cik.no = 38079, filing.year = 2005, useragent)

tail(output)
```

## Generate sentiment measures of SEC filings
The `getSentiment` function takes CIK(s), form type(s), and year(s) as input parameters. The function first imports available downloaded filings in the local working directory `Edgar filings_full text` created by getFilings function; otherwise, it automatically downloads the filings which are not already been downloaded. It then reads, cleans, and computes sentiment measures for these filings. The function returns a dataframe with filing information and sentiment measures.
```{r}
senti.df <- getSentiment(cik.no = c('1000180', '38079'), form.type = '10-K', filing.year = 2006, useragent) 

senti.df
```

Following are the definitions of the text characteristics and the sentiment measures:

`file.size` = The filing size of a complete filing on the EDGAR server in kilobyte (KB).

`word.count` = The total number of words in a filing text, excluding HTML tags and exhibits text.

`unique.word.count` = The total number of unique words in a filing text, excluding HTML tags and exhibits text.

`stopword.count` = The total number of stop words in a filing text, excluding exhibits text.

`char.count` = The total number of characters in a filing text, excluding HTML tags and exhibits text.

`complex.word.count` = The total number of complex words in the filing text. When vowels (a, e, i, o, u) occur more than three times in a word, then that word is identified as a complex word.

`lm.dictionary.count` = The number of words in the filing text that occur in the Loughran-McDonald (LM) master dictionary.

`lm.negative.count` = The number of LM financial-negative words in the document.

`lm.positive.count` = The number of LM financial-positive words in the document.

`lm.strong.modal.count` = The number of LM financial-strong modal words in the document.

`lm.moderate.modal.count` = The number of LM financial-moderate Modal words in the document.

`lm.weak.modal.count` = The number of LM financial-weak modal words in the document.

`lm.uncertainty.count` = The number of LM financial-uncertainty words in the document.

`lm.litigious.count` = The number of LM financial-litigious words in the document.

`hv.negative.count` = The number of words in the document that occur in the 'Harvard General Inquirer' Negative word list, as defined by LM.
